\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
%\documentclass{cslthse-msc} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{amsfonts}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{float}
\usepackage{multirow}
\usepackage{multicol}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}
\usepackage{natbib}

% Added by Gustaf
\usepackage{enumerate}
\usepackage{subcaption}


% used to display the used files at the end. Select nofilelist as a package option to disable this
\listfiles % initialize


%\geometry{showframe}
%better like this?
\student{Gustaf Backman}{ine14gba@student.lu.se}

\thesisnumber{LU-CS-EX: 2020-XX} % Birger Swahn will provide this number to you, once the thesis is ready for publication

\title{Forecasting Financial Indices from Financial News}

\threelinestitle


\subtitle{SUBTITLE}\marginpar{Have a subtitle or remove it}
\company{Kidbrooke Advisory AB}
\supervisors{Pierre Nugues, \href{mailto:pierre.nugues@cs.lth.se}{\texttt{pierre.nugues@cs.lth.se}}}{Edvard Sjögren, \href{mailto:edvard.sjogren@kidbrooke.com}{\texttt{edvard.sjogren@kidbrooke.com}}}
\examiner{Marcus Klang, \href{mailto:marcus.klang@cs.lth.se}{\texttt{marcus.klang@cs.lth.se}}}

\date{\today}

\acknowledgements{TACK
}

\theabstract{
In the last few years the capability of natural language processing has increased greatly. The implications this methodical leap has for different areas is yet to be explored. In this thesis, I have evaluated the predictive power of financial news headlines on the movement of financial indices. More specifically, I tried to determine if I could improve a traditional time series model by adding news data. In my experiments, I used text representations of different complexities, from TF-IDF to recent transformer models, such as BERT and Sentence-BERT and, as targets, the S\&P 500 and US treasury rates with one and three years maturity. 

My findings suggest that no model can predict the movement of treasury rates based on news data, but the classification performance for the S\&P 500 is well over a random baseline. The best model using the TF-IDF word representation and a random forest classifier could reach an accuracy of 59.1\%. 

Furthermore, adding news data can predict better than a random baseline whether a time series forecast is too high or too low. This applies to all indices. I could reach an accuracy of 64.1 \% with SBERT feature extraction and logistic regression. 
}

\keywords{NLP, fintech, deep learning, time series analysis, transformers. }

%% Only used to display font sizes
\makeatletter
\newcommand\thefontsize[1]{{#1 \f@size pt\par}}
\makeatother
%%%%%%%%%%

\begin{document}
\renewcommand{\bibname}{References}

\makefrontmatter
\include{Chapters/Problem_Description}
\include{Chapters/Theoretical_Background}
\include{Chapters/Method}
\include{Chapters/Results}
\include{Chapters/Discussion}

% Should use consistent formatting when it comes to Names ("FirstName LastName", or "F. LastName")
%\printbibliography
\makebibliography{MyMSc} % See file MyMSc

\begin{appendices}

\include{Chapters/AppendixA}
\include{Chapters/AppendixB}

% display used packages information unless noflielist is used in the cslthse-msc package option
\printfilelist

%make sure we're on even page with the pop-sci
\checkoddpage
\ifoddpage
\else
   \newpage
   \thispagestyle{empty}
   \mbox{ }
\fi
%\includepdf[pages={1}]{popsci/popsci.pdf}
\end{appendices}

\end{document}