\chapter{List of Changes}

\subsubsection{Since 2019/10/30}
\begin{itemize}
\item Bibliography is now called References. This can be easily adjusted by changing \\ \verb+\renewcommand{\bibname}{References}+ after \verb+\begin{document}+.
\end{itemize}

\subsubsection{Since 2019/04/01}
\begin{itemize}
\item Added the \texttt{nofilelist} option in to the package. By default the list of packages is displayed at the end of the document, before the pop-sci. With the option, the file list is not displayed. Used mainly for debug purposes. Ignore warnings and the two errors about the \texttt{fontenc.sty}
\end{itemize}

\subsubsection{Since 2018/11/21}
\begin{itemize}
\item Added the report cover to the template (along with the archive cover, as the 2nd page). This includes the front cover and back as the pop-sci article. Once the report is ready for print, the authors will receive a report number, of the format \texttt{LU-CS-EX 2019-NN}. Generate the report using this number in the template, to get a print-ready pdf.
\item Changed both the report and pop-sci template to use \verb+\student+ or \verb+\students+ commands instead of \verb+\author+.
\item Clarified the difference between {\em Results} and {\em Discussion} sections in a report.
\item Added more information about the use of {\em References}.
\item Added {\em LTH} colours in the template and description in {\em Colours}.
\end{itemize}

\subsubsection{Since 2016/04/29}
\begin{itemize}
\item A better template for the popular science summary, by Magnus Hultin.
\end{itemize}

\subsubsection{Since 2015/09/11}
\begin{itemize}
\item Added a template for the popular science summary, in the \verb+popsci+ directory.
\item Added code in the report that imports the one page popular science \texttt{pdf} at the end of the document.
\end{itemize}

\subsubsection{Since 2015/04/27}
\begin{itemize}
\item Improved the \textbf{Structure} chapter and added more detailed comments for each part.
\end{itemize}

\subsubsection{Since 2014/02/18}
\begin{itemize}
\item Added the possibility to specify two supervisors. Use either of the \verb+\supervisor{}+ or \verb+\supervisors{}{}+ commands to set the names and contacts on the first page.
\end{itemize}

\subsubsection{Since 2013/09/23}
\begin{itemize}
\item Added missing colon ":" after \textit{Examiner} on the front page. 
\end{itemize}

\subsubsection{Since 2013/08/30}
\begin{itemize}
\item Changed fonts from Garamond ( Times New Roman ), Helvetica ( Arial ), Courier ( Source Code Pro ) to Tex Gyre fonts, namely Termes, Heros, Cursor, which are freely available with TexLive 2013 installation. These are all clones of Times New Roman, Helvetica and Courier, respectively. Garamond is problematic on some systems, being a non-freely available font.
\item Corrected the \textit{Face} column in Table \ref{tab:fonts} to correctly depict the font face.
\end{itemize}

\subsubsection{Since 2013/02/22}
\begin{itemize}
\item Number of words required in the abstract changed to 150 (from 300).
\end{itemize}

\subsubsection{Since 2013/02/15}
\begin{itemize}
\item Made a separate document class, for clarity.
\item made it work with pdfLaTeX and garamond.sty, in addition to XeLaTeX and true type fonts. It is up to the user to get the hold of the garamond.zip from \url{http://gael-varoquaux.info/computers/garamond/index.html}.
\end{itemize}